Fast Hyperparameter Selection for Graph Kernels via Subsampling and\\Multiple Kernel Learning

### 2017-02-07 paper.tex
tabella sistemata

In the algorithm, we adopted Python's list comprehension notation. We used the following functions:  $random\_subset\_of(tr,p_S)$  samples a percentage $p_S$ of the examples in the set $Tr$; $Gram(S,k)$ computes the \textit{Gram} matrix of the kernel $k$ on the set of examples $Tr$; \textit{EasyMKL($K_s$)} computes a list of weights (one for each kernel in $K_s$) according to the EasyMKL algorithm; $top_of(L,\hat{\boldsymbol{\eta}},p_K)$ extracts the top $p_K$ percentage of the elements in $L$ according to the weights $\hat{\boldsymbol{\eta}}$.

@@

\begin{table}[]
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{l|c|ccc|ccc}
\hline\hline
dataset & \# train &\kval &\kmkl &\ksum & \ksmkl & \kssum & \ksw \\
\hline
MUTAG   & 188 & \res{0.9023}{0.075} & \res{0.9310}{0.061} & \res{0.9309}{0.060} & \res{0.9292}{0.054} & \res{0.9292}{0.054} & \res{\tb{0.9331}}{0.053}    \\
&			  & 18m					& 40m				& 8m		& 3m		&4m		&4m\\\hline
CPDB    & 684 &$0.8753_{\pm0.029}$ & $0.8814_{\pm0.027}$ & $0.8809_{\pm0.029}$ & $0.8768_{\pm0.023}$ & $\tb{0.8850}_{\pm0.027}$ & $0.8751_{\pm0.023}$ \\
&			  & 1h 16m				& 8h 33m		& 20m	& 1h 37m		& 5m		&5m\\\hline
GDD     & 1178 & \res{0.8647}{0.045} & \res{\tb{0.8719}}{0.039} & \res{0.8675}{0.039} & \res{0.8690}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
&			& $>$100h	& $>$100h	& $>$100h	&3h		& 4h 15m		& 4h 15m\\\hline
AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{\tb{0.7845}}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\
&		& 6h 39m		& 50h	& 2h 44m		& 11h 10m	& 1h 4m	& 1h 4m\\\hline
NCI1    & 4110 & \res{0.8839}{0.043} & - & \res{\tb{0.8851}}{0.041} & \res{0.8818}{0.043} & \res{0.8772}{0.047} & \res{0.8811}{0.044}    \\
&	&	39h	&-	& 7h 24m		& 98h	& 2h 1m	& 2h 1m\\\hline
NCI109 & 4127 & \res{\tb{0.8728}}{0.025} & - & \res{0.8713}{0.025} & \res{0.8670}{0.024}  & \res{0.8713}{0.025} & \res{0.8680}{0.022}  \\
&	&	44h	&-	& 7h 36m		& 99h	& 1h 47m	& 1h 47m\\\hline
CAS     & 4337 & \res{0.9189}{0.012} & - & \res{\tb{0.9209}}{0.012} & \res{0.9195}{0.011} & \res{0.9161}{0.012} & \res{0.9185}{0.012}    \\
&	&	38h	&-	& 4h 26m		&$>$100h	& 1h 34m		& 1h 34m\\	%176h
\hline\hline
\end{tabular}}
\caption{AUC score, standard deviation and computational time for all baselines and all subsampling proposed methods.}
\label{tab:res}
\end{table}

>>>>

In the algorithm, we adopted Python's list comprehension notation. We used the following functions:  $random\_subset\_of(Tr,p_S)$  samples a percentage $p_S$ of the examples in the set $Tr$; $Gram(Tr,k)$ computes the \textit{Gram} matrix of the kernel $k$ on the set of examples $Tr$; \textit{EasyMKL($K_s$)} computes a list of weights (one for each kernel in $K_s$) according to the EasyMKL algorithm; $top\_of(L,\hat{\boldsymbol{\eta}},p_K)$ extracts the top $p_K$ percentage of the elements in $L$ according to the weights $\hat{\boldsymbol{\eta}}$.

@@

%\begin{table}[]
%\centering
%\resizebox{\textwidth}{!}{
%\begin{tabular}{l|c|ccc|ccc}
%\hline\hline
%dataset & \# train &\kval &\kmkl &\ksum & \ksmkl & \kssum & \ksw \\
%\hline
%MUTAG   & 188 & \res{0.9023}{0.075} & \res{0.9310}{0.061} & \res{0.9309}{0.060} & \res{0.9292}{0.054} & \res{0.9292}{0.054} & \res{\tb{0.9331}}{0.053}    \\
%&			  & 18m					& 40m				& 8m		& 3m		&4m		&4m\\\hline
%CPDB    & 684 &$0.8753_{\pm0.029}$ & $0.8814_{\pm0.027}$ & $0.8809_{\pm0.029}$ & $0.8768_{\pm0.023}$ & $\tb{0.8850}_{\pm0.027}$ & $0.8751_{\pm0.023}$ \\
%&			  & 1h 16m				& 8h 33m		& 20m	& 1h 37m		& 5m		&5m\\\hline
%GDD     & 1178 & \res{0.8647}{0.045} & \res{\tb{0.8719}}{0.039} & \res{0.8675}{0.039} & \res{0.8690}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
%&			& $>$100h	& $>$100h	& $>$100h	&3h		& 4h 15m		& 4h 15m\\\hline
%AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{\tb{0.7845}}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\
%&		& 6h 39m		& 50h	& 2h 44m		& 11h 10m	& 1h 4m	& 1h 4m\\\hline
%NCI1    & 4110 & \res{0.8839}{0.043} & - & \res{\tb{0.8851}}{0.041} & \res{0.8818}{0.043} & \res{0.8772}{0.047} & \res{0.8811}{0.044}    \\
%&	&	39h	&-	& 7h 24m		& 98h	& 2h 1m	& 2h 1m\\\hline
%NCI109 & 4127 & \res{\tb{0.8728}}{0.025} & - & \res{0.8713}{0.025} & \res{0.8670}{0.024}  & \res{0.8713}{0.025} & \res{0.8680}{0.022}  \\
%&	&	44h	&-	& 7h 36m		& 99h	& 1h 47m	& 1h 47m\\\hline
%CAS     & 4337 & \res{0.9189}{0.012} & - & \res{\tb{0.9209}}{0.012} & \res{0.9195}{0.011} & \res{0.9161}{0.012} & \res{0.9185}{0.012}    \\
%&	&	38h	&-	& 4h 26m		&$>$100h	& 1h 34m		& 1h 34m\\	%176h
%\hline\hline
%\end{tabular}}
%\caption{AUC score, standard deviation and computational time for all baselines and all subsampling proposed methods.}
%\label{tab:res}
%\end{table}

\begin{table}[]
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{l|c|ccc|ccc}
\hline\hline
dataset & \# train &\kval &\kmkl &\ksum & \ksmkl & \kssum & \ksw \\
\hline
MUTAG   & 188 & \res{0.90}{0.08} & \res{0.93}{0.06} & \res{0.93}{0.06} & \res{0.93}{0.05} & \res{0.93}{0.05} & \res{0.93}{0.05}    \\
&			  & 18m					& 40m				& 8m		& 3m		&4m		&4m\\\hline
CPDB    & 684 & \res{0.88}{0.03} & \res{0.88}{0.03} & \res{0.88}{0.03} & \res{0.88}{0.02} & \res{0.89}{0.03} 	& \res{0.88}{0.02} \\
&			  & 1h 16m				& 8h 33m		& 20m	& 1h 37m		& 5m		&5m\\\hline
GDD     & 1178 & \res{0.86}{0.05} & \res{0.87}{0.04} & \res{0.87}{0.04} & \res{0.87}{0.04} & \res{0.87}{0.04} & \res{0.80}{0.04}    \\
&			& $>$100h	& $>$100h	& $>$100h	&3h		& 4h 15m		& 4h 15m\\\hline
AIDS    & 1503 & \res{0.78}{0.08} & \res{0.78}{0.08} & \res{0.78}{0.08} & \res{0.78}{0.08} & \res{0.77}{0.07} & \res{0.77}{0.07}    \\
&		& 6h 39m		& 50h	& 2h 44m		& 11h 10m	& 1h 4m	& 1h 4m\\\hline
NCI1    & 4110 & \res{0.88}{0.04} & - & \res{0.89}{0.04} & \res{0.88}{0.04} & \res{0.88}{0.05} & \res{0.88}{0.04}    \\
&	&	39h	&-	& 7h 24m		& 98h	& 2h 1m	& 2h 1m\\\hline
NCI109 & 4127 & \res{0.87}{0.03} & - & \res{0.87}{0.03} & \res{0.87}{0.02}  & \res{0.87}{0.03} & \res{0.87}{0.02}  \\
&	&	44h	&-	& 7h 36m		& 99h	& 1h 47m	& 1h 47m\\\hline
CAS     & 4337 & \res{0.92}{0.01} & - & \res{0.92}{0.01} & \res{0.92}{0.01} & \res{0.92}{0.01} & \res{0.92}{0.01}    \\
&	&	38h	&-	& 4h 26m		&$>$100h	& 1h 34m		& 1h 34m\\	%176h
\hline\hline
\end{tabular}}
\caption{AUC score, standard deviation and computational time for all baselines and all subsampling proposed methods.}
\label{tab:res}
\end{table}
